
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
\documentclass{article}

% references each of data structure topics to book pages

\def\range#1#2#3{Section~#1, pages:~#2--#3.\newline}

\begin{document}

\section{Analysis of Algoritms}

\subsection{Criteria of complexity in time and space}

\subsection{Asymptotic notation}
\cite{taocp1}~\range{1.2.11}{107}{123}
\cite{graham}~\range{9}{439}{488}
\cite{szwarcfiter}~\range{1.5}{10}{12}

\section{Sorting}

\subsection{Insertion}

\cite{taocp3}~pg~80\\
Comparison analysis~\cite{taocp1}

\section{Paradigms of projects of algorithms}

\subsection{Induction}
\cite{taocp1}~\range{1.2.1}{11}{20}
\cite{milies}~\range{1.3}{24}{34}

\section{Graphs and data structures to represent them}
\noindent introduction \\
\cite{dasgupta}~\range{3.1}{80}{82}
\noindent representation\\
\cite{szwarcfiter}~\range{2.9}{68}{71}


\subsection{Recursivity}
\cite{szwarcfiter}~\range{1.3}{4}{6}


\begin{thebibliography}{}

\bibitem[Coelho and Milies, 2001]{milies}
Coelho, S.~P. and Milies, C.~P. (2001).
\newblock {\em Numeros: Uma Introduçao a Matematica}.
\newblock Edusp, 3$^a$ edition.

\bibitem[Dasgupta et~al., 2009]{dasgupta}
Dasgupta, S., Papadimitriou, C., and Vazirani, U. (2009).
\newblock {\em Algoritmos}.
\newblock McGraw-Hill Brasil.

\bibitem[Graham et~al., 1994]{graham}
Graham, R.~L., Knuth, D.~E., and Patashnik, O. (1994).
\newblock {\em Concrete Mathematics: A Foundation for Computer Science}.
\newblock Addison-Wesley Professional, 2nd edition.

\bibitem[Knuth, 1997]{taocp1}
Knuth, D.~E. (1997).
\newblock {\em Fundamental Algorithms}, volume~1 of {\em The Art of Computer
  Programming}.
\newblock Addison--Wesley, Reading, Massachusetts, second edition.

\bibitem[Knuth, 1998]{taocp3}
Knuth, D.~E. (1998).
\newblock {\em The art of computer programming}, volume~3.
\newblock Addison-Wesley Longman Publishing Co., Boston, MA, USA, 2nd edition.

\bibitem[Szwarcfiter and Markenzon, 1994]{szwarcfiter}
Szwarcfiter, J.~L. and Markenzon, L. (1994).
\newblock {\em Estruturas de Dados e seus Algoritmos}.
\newblock LTC.

\end{thebibliography}


\end{document}
